---
title: "30 day Map challenge"
output:
  html_document:
    df_print: paged
---

These are my submissions for the 30 day map challenge. All the maps were created using R.

```{r}
library(leaflet)
library(rgdal)
library(htmlwidgets)
```

```{r}
#### This reads the shapefile of cnetral Indian landscape in R 
cil <-readOGR("D:/Global rasters/Central Indianb Landscape.kml")
```

I created an icon for marker in the leaflet package. Any image can be used as a marker in leaflet. The process is shown below in the codes.
```{r}
treeIcons <- iconList(
  tree = makeIcon("C:/Users/HP/Documents/tree_icon.png","tree_icon.png", 64, 64)
)
```

## The final map output

This is the polygon of the Central Indian Landscape highlighted in the blue colour. The basemap is downloaded from the website mentioned here. I did not use the default openstreetmap as the basemap.

```{r}
m1 <- leaflet(cil) %>%
  addTiles(urlTemplate = "https://{s}.tile.opentopomap.org/{z}/{x}/{y}.png") %>%  ##Add  map tiles
   addPolygons(color = "blue") %>% ## Add shapefile
  addMarkers(lng=79.56, lat=22.5076, label ="Central Indian Landscape", icon = treeIcons,
             labelOptions = labelOptions(noHide = T, textsize = "18px"))

m1
```

